---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

**NOTE: This is a toy package created for expository purposes. It is not meant to actually be useful. If you want a package for factor handling, please see [forcats](https://cran.r-project.org/package=forcats).**

## Reorderv2
Graphing factors tend to be messy, since they are usually misaligned. Reorder is a function used to order factors in ascending order. Reorderv2 is a package which will order factors in descending order.

### Installation
```{r}
devtools::install_github("myuen89/reorderv2")
```

### Quick demo
Reordering factor levels in descending order. Will not work if input is not of class factor 
```{r}
library(dplyr)
library(reorderv2)

x <- factor(c('leopard', 'kilo', 'gryphon', 'foxtrot'))
y <- factor(c('foxtrot', 'gryphon', 'kilo', 'leopard'))
z <- c("hello", "blue", "cake", "wall")

reorder_desc(x)
as.character(y)
reorder_desc(z)
```


